|

### 2023-01-11 paper_comparison/paper_comparison/paper_comparison.Rmd
update wording up to Section 2.1. In particular, - change "one" to "we" (it's a cop out not to include us, and don't make it sound like it's about someone distant) - change Plot A of Figure 1 to Figure 1A say. - update about violation of normality. Original logical argument is not correct.

One can access residuals in multiple ways. Residuals might be plotted, as a histogram or quantile-quantile plot to examine the distribution. Using the classical normal linear regression model as an example, if the distribution is symmetric and unimodal, it is well-behaved. But if the distribution is skewed, bimodal, multimodal, or contains outliers, there is cause for concern. One could also inspect the distribution by conducting a goodness of fit test, such as the Shapiro-Wilk Normality test [@shapiro1965analysis].

@@

Graphical summaries in which residuals are plotted against fitted values or other functions of the regressors that are approximately orthogonal to residuals are referred to as standard residual plots in @cook1982residuals. As shown in Figure \ref{fig:residual-plot-common-departures}, the plot A is an ideal residual plot with residuals evenly distributed at both sides of the horizontal zero line, with no noticeable patterns.

@@

Non-linearity is a type of model misspecification caused by failing to include higher order terms of the regressors in the regression equation. Any non-linear functional form of residuals on fitted values presented in the residual plot could be considered as an indicative of non-linearity. An example residual plot containing visual pattern of non-linearity is given at plot B of Figure \ref{fig:residual-plot-common-departures}. One can clearly observe the "S-shape" from the residual plot as the cubic term is not captured by the misspecified model.

Heteroskedasticity refers to the presence of nonconstant error variance in a regression model. It is mostly due to the strict but false assumptions on the variance-covariance matrix of the error term. The usual pattern of heteroskedasticity on a residual plot is the inconsistent spread of the residuals across the horizontal axis. Visually, it sometimes results in the so-called "butterfly" shape as shown in the plot C of Figure \ref{fig:residual-plot-common-departures}, or the "left-triangle" and "right-triangle" shape where the smallest variance occurs at one side of the horizontal axis.

Compared to non-linearity and heteroskedasticity, non-normality is usually harder to detect from a residual plot since a scatter plot do not readily reveal the marginal distribution. A favourable graphical summary for this task is the quantile-quantile plot. Hence, non-normality will not be the focus of this paper as we mainly discuss residual plots. For a consistent comparison, the residual plot of this departure is still presented in plot D of Figure \ref{fig:residual-plot-common-departures}. Besides, it is important to note that not all regression models assume normality for the error term, but a certain amount do including the classical normal linear regression model. In the case that the normality assumption is violated, it is expected to observe data points do not center around the horizontal axis and there is an uneven distribution of the number points at both below and above the horizontal axis. For example, given a skewed error distribution, there will be fewer data points and more outliers on one side of the horizontal axis as shown in plot D of Figure \ref{fig:residual-plot-common-departures}.

>>>>

We can assess residuals in multiple ways. Residuals might be plotted, as a histogram or quantile-quantile plot to examine the distribution. Using the classical normal linear regression model as an example, if the distribution is symmetric and unimodal, we consider it well-behaved. But if the distribution is skewed, bimodal, multimodal, or contains outliers, there is cause for concern. One could also inspect the distribution by conducting a goodness of fit test, such as the Shapiro-Wilk Normality test [@shapiro1965analysis].

@@

Graphical summaries in which residuals are plotted against fitted values or other functions of the regressors that are approximately orthogonal to residuals are referred to as standard residual plots in @cook1982residuals. Figure \ref{fig:residual-plot-common-departures}A shows an ideal residual plot with residuals evenly distributed at both sides of the horizontal zero line, with no noticeable patterns.

@@

Non-linearity is a type of model misspecification caused by failing to include higher order terms of the regressors in the regression equation. Any non-linear functional form of residuals on fitted values in the residual plot could be indicative of non-linearity. An example residual plot containing visual pattern of non-linearity is given at Figure \ref{fig:residual-plot-common-departures}B. One can clearly observe the "S-shape" from the residual plot as the cubic term is not captured by the misspecified model.

Heteroskedasticity refers to the presence of nonconstant error variance in a regression model. It is mostly due to the strict but false assumptions on the variance-covariance matrix of the error term. The usual pattern of heteroskedasticity on a residual plot is the inconsistent spread of the residuals across the horizontal axis. Visually, it sometimes results in the so-called "butterfly" shape as shown in the Figure \ref{fig:residual-plot-common-departures}C, or the "left-triangle" and "right-triangle" shape where the smallest variance occurs at one side of the horizontal axis.

Compared to non-linearity and heteroskedasticity, non-normality is usually harder to detect from a residual plot since a scatter plot do not readily reveal the marginal distribution. A favourable graphical summary for this task is the quantile-quantile plot. As we mainly discuss residual plots, non-normality will not be the focus of this paper. For a consistent comparison, the residual plot of this departure is still presented in Figure \ref{fig:residual-plot-common-departures}D. When the number residuals below and above the horizontal axis are uneven across the local regions along the $x$-axis, we expect that the normality assumption is violated. For example, given a skewed error distribution, there will be fewer data points and more outliers on one side of the horizontal axis as shown in Figure \ref{fig:residual-plot-common-departures}D.
